---
title: "Task-01"
output:
  pdf_document: default
  html_document: default
---

Name : Imanuel Adipranata

ID : 22056482

Github : <https://github.com/22056482/R_Project>

**Importing necessary libraries**

```{r}
library(dplyr)
library(knitr)
```

**Loading Data**

```{r}
user_data <- read.csv("../data/users.csv")
head(user_data)
```

As you can see there are several missing value on the data. We need to assign NA value to the missing data because R will read that as empty string ("")

```{r}
user_data[user_data == ""] <- NA
```

Since each entity can already be identified using *user_id*, the *name* column can be ignored.

```{r}
user_data <- subset(user_data, select = -name)
```

**NA Handling**

```{r}
colSums(is.na(user_data)) # print count of NA value for each columns
```

There is one missing value in the *user_id* column and 1160 missing values in the *member_since* column. We can remove the row that does not have a *user_id*.

```{r}
(1160 / nrow(user_data)) * 100 # calculate proportion of missing value on member_since column
```

Since the proportion of missing values in the member_since column is only around 3%, we can also remove the rows with missing values in that column.

```{r}
user_data <- na.omit(user_data) # remove row with NA value
colSums(is.na(user_data)) # check again NA value on user_data
```

**Grouping**

The users will be grouped into 3 group: Veteran, Intermediate and New (based on their member since date) before 2017, between 2017-2022, and after 2022 respectively.

```{r}
user_data <- user_data %>%
  mutate(
    # Extract the year from the date string and convert it to a numeric format
    year_joined = as.integer(substr(member_since, 1, 4)),
    
    # Create a column called member_category based on the year_joined
    member_category = case_when(
      year_joined < 2017 ~ "Veteran",
      year_joined >= 2017 & year_joined <= 2022 ~ "Intermediate",
      year_joined > 2022 ~ "New"
    )
  )
user_data <- subset(user_data, select = -year_joined) # remove year_joined column

head(user_data)
```

**Data Exploratory**

```{r}
summary(user_data)
```

```{r}
# Calculate the frequency of each member category
category_counts <- table(user_data$member_category)

# Calculate the percentage for each category
percentages <- round(100 * category_counts / sum(category_counts), 1)

# Create a new label that includes both the category name and its percentage
labels_with_percentages <- paste(names(category_counts), "\n", percentages, "%", sep = "")

colors <- c("skyblue", "skyblue2","skyblue3")

pie(category_counts,
    labels = labels_with_percentages,
    main = "Distribution of Member Categories",
    col = colors,
    border = "white",
    cex = 1) # font size
```

```{r}
boxplot(review_count ~ member_category, # formula = y - group
        data = user_data,
        xlab = "Member Categories",
        ylab = "Review Count",
        main = "Boxplot of Review Counts by Member Category",
        col = "skyblue",
        border = "black"
)
```

This plot indicates that all three categories have a similar range and median of review counts, suggesting no major difference in review activity based on member category.

```{r}
boxplot(average_stars ~ member_category, # formula = y - group
        data = user_data,
        xlab = "Member Categories",
        ylab = "Review Count",
        main = "Boxplot of Average Review Stars by Member Category",
        col = "skyblue",
        border = "black"
)
```

```{r}
summary_table <- user_data %>%
  group_by(member_category) %>%
  summarise( # calcullation for each categories
    user_count = n(), # calculate user count
    avg_review_count = mean(review_count), # averaging rata-rata review_count
    avg_average_stars = mean(average_stars) # averaging average_stars
  ) %>%
  # rename columns
  rename(
    "Member Categories" = member_category,
    "Users" = user_count,
    "Average Review Count" = avg_review_count,
    "Average Review Stars" = avg_average_stars
  )

kable(summary_table,
      caption = "User Data Summary by Member Category",
      format = "pipe",
      align = "c")
```

The conclusion is that there are no significant differences between each user group. However, there is a considerable difference in the number of users in each group.
