---
title: "Task-03"
output:
  pdf_document: default
  html_document: default
---

**Import necessary libraries**

```{r}
library(dplyr)
library(ggplot2)
library(knitr)
```

**Loading data**

```{r}
reviews <- read.csv("../data/reviews.csv", stringsAsFactors = FALSE)
```

**Identify the 10 users who have written the most reviews**

Identify the 10 most active users by counting the number of reviews per *user_id* from the reviews dataset, sorting them in descending order based on the number of reviews, and selecting the top 10 users *top_users_by_count*. Next, filters the original reviews dataset to include only reviews from these top 10 users *reviews_from_top_users*. After that, for each of the 10 users, the algorithm calculates the average star rating they have given, ignoring any missing values NA in the calculation *average_stars_for_top_users*.

```{r}
top_users_by_count <- reviews %>%
  group_by(user_id) %>%
  summarise(review_count = n(), .groups = 'drop') %>% # Group the rows in the reviews dataset by the user_id column
  arrange(desc(review_count)) %>% # sorting the results
  slice_head(n = 10) # get 10 rows

reviews_from_top_users <- reviews %>%
  filter(user_id %in% top_users_by_count$user_id)

# calculate average stars for each of these top users.
# na.rm = TRUE ensures that NA values in the 'stars' column are ignored during mean calculation.
average_stars_for_top_users <- reviews_from_top_users %>%
  group_by(user_id) %>%
  summarise(average_stars = mean(stars, na.rm = TRUE), .groups = 'drop')

print(average_stars_for_top_users)
```

Then, merges *left_join* the review count information *top_users_by_count* with the average star ratings *average_stars_for_top_users* for each user into a single summary table called *summary_top_users*, which is then sorted again based on the number of reviews

```{r}
summary_top_users <- top_users_by_count %>%
  left_join(average_stars_for_top_users, by = "user_id") %>%
  arrange(desc(review_count)) # Re-arrange to ensure order by review_count

summary_table <- kable(summary_top_users,
                              caption = "Top 10 Users: Review Count and Average Stars",
                              col.names = c("User ID", "Total Reviews", "Average Stars"),
                              align = "c",    # Center align columns
                              digits = 2,     # Round average stars to 2 decimal places
                              format = "pipe") # Use "pipe"

print(summary_table)
```

**Visualize**

```{r}
# Ensure that the order of users in the plot is consistent with the previous summary table
reviews_from_top_users$user_id <- factor(reviews_from_top_users$user_id,
                                         levels = summary_top_users$user_id)

# Create the boxplot
# na.rm = TRUE in geom_boxplot will ensure NA star values are ignored for plotting
rating_distribution_plot <- ggplot(reviews_from_top_users,
                                   aes(x = user_id,
                                       y = stars,
                                       fill = user_id)) +
  geom_boxplot(na.rm = TRUE) +
  labs(title = "Star Rating Distribution for Top 10 Users",
       x = "User ID",
       y = "Stars Given") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1), # Rotate x-axis labels for readability
        legend.position = "none")  + # Hide legend 
  coord_cartesian(ylim = c(0, 6))

print(rating_distribution_plot)

```

The boxplot shows how the top users vary in the way they give star ratings. Users such as u_6766 and u_27907 tend to give higher ratings overall, with medians above 3 and upper quartiles close to 5. In contrast, users like u_17629 and u_22933 give lower ratings more frequently, as indicated by their lower medians and compressed upper ranges. Some users show wide variability (e.g., u_6766, u_27907), while others have more consistent rating patterns (e.g., u_14899). Outliers in a few users suggest occasional extreme ratings.
